A Review of Lossless Data Compression Methods

### 2018-11-17 paper.tex
Update with DEFLATE RFC.

The Lempel-Ziv compression algorithm, commonly referred to as LZ77 or
LZ78 for short, is one of the most widespread compression schemes in
use, especially when including its large family of derivative
methods. It was first introduced in 1977. \cite{LempelZiv} Algorithms
based on the Lempel-Ziv algorithms are relatively efficient and work
well with a wide variety of inputs.

The algorithm is based on a dictionary-style approach; that is to say,
it creates a dictionary of codewords within the input bit-string
as the algorithm progresses.

@@

The Lempel-Ziv-Welch compression algorithm was an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. \cite{LempelZivWelch}

>>>>

The Lempel-Ziv compression algorithm, commonly referred to as LZ77 or
LZ78, or even simply LZ for short, is one of the most widespread
compression schemes in use, especially when including its large family
of derivative methods. It was first introduced in
1977. \cite{LempelZiv} Algorithms based on the Lempel-Ziv algorithms
are relatively efficient and work well with a wide variety of inputs.

The algorithm is based on a dictionary-style approach; that is to say,
it creates a dictionary of codewords within the input data as the
algorithm progresses. Lempel-Ziv uses a ``sliding-window'' technique
to construct its dictionary. For each set of bytes it attempts to
compress, it inspects its sliding window, which extends some set
amount behind the bytes under consideration. In this way, the
algorithm builds a prefix code as it proceeds through the file. A
``prefix'' can be one or more characters long. For each point in the
input data, the algorithm consults the prefix table of prefixes
contained in the sliding window, which is a set amount of data prior
to the current point. If the current prefix is found in the prefix
table, the algorithm outputs a data triplet indicating how far back in
the window the prefix occurred, the length of the prefix, and finally
the character which comes after the prefix. This means that the very
first characters in the input data will be encoded as 1-character
prefixes. (For our very first characters in the input data, since
there can't be any prefixes in the sliding window yet, the encoded
form will consist of zero-length prefixes followed by the input
character literals.)

The basic method introduced in Lempel and Ziv's original paper is
vulnerable to some significant drawbacks. Since each individual byte
in the input can take up at most three bytes in the output, it is
possible that some pathological input data can have a compressed form
which is substantially larger, especially if the sliding window is
small. As such, this suggests a good jumping-off point for creating
improvements upon the original algorithm.

@@

The Lempel-Ziv-Welch compression algorithm was an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. \cite{LempelZivWelch} The LZW variant is
extremely widespread in applications; for instance, one of its many
uses is as part of the GIF image format.

\subsection{DEFLATE}

Another algorithm based on the Lempel-Ziv foundation is the DEFLATE
algorithm, codified in RFC 1951. \cite{RFC1951}
